Species with high control capacity support stable coexistence of pollination networks

### 2018-07-18 paper/manuscript.Rmd
Settle on a title
Remove superior nodes stuff from the methods and the results

*Alternative titles:*

* Structural controllability of ecological networks
* Structural controllability: species with high control capacity support stable coexistence of pollination networks

@@

In addition, we wanted to understand how two species-level control metrics are related to five metrics of keystoneness based on centrality. 
For the centrality metrics, we use a species' degree, betweenness, closeness centrality [@martin_gonzalez_centrality_2010], page rank [@mcdonald-madden_using_2016], and eigen centrality [@jordano_ecological_2006]. 
The first control metric we use is a species control capacity $\phi$ described above. 
The second metric is the probability that a focal species influences the abundance of another species internally, regardless of whether a management intervention is required in that species or not. 
We call this the probability of being a superior node $\sigma$. 
Because superior nodes are those at the beginning of a matched link, \(\sigma\) could be seen as a "softer" version of control capacity. 
Conveniently, unlike the minimum driver-node set, superior species are the same for all control configurations and so in a network without reciprocal links the probability that a species is superior $\sigma$ is either 1 or 0.

@@

Species control capacity $\phi$ was only weakly correlated with commonly-used centrality metrics. 
The Spearman correlation between these ranged between `r round(min(correlations$control_capacity), 2)` (with betweeness-centrality) and `r round(max(correlations$control_capacity), 2)` (with eigen-centrality). 
On the other hand, the probability of being a superior species $\sigma$ was slightly more correlated to established centrality metrics as its Spearman correlation ranged between `r round(min(correlations$superior), 2)` (with eigen-centrality) and `r round(max(correlations$superior), 2)` (with degree; Figure \@ref(S-fig:fig-correlogram)). 
Despite the higher correlation with species' degree we still observed many species with a low degree and a high probability of being superior nodes (Figure \@ref(S-fig:fig-species-models-degree)b).

>>>>

<!-- *Alternative titles:*  -->
<!-- * Structural controllability of ecological networks -->

@@

In addition, we wanted to understand how a species control capacity $\phi$ described above relates to metrics of keystoneness based on centrality. 
Specifically, in each network, we calculated the species' degree, betweenness, closeness centrality [@martin_gonzalez_centrality_2010], page rank [@mcdonald-madden_using_2016], and eigen centrality [@jordano_ecological_2006]. 
We then calculated the spearman correlation coefficient between control capacity and each of these centrality metrics.

@@

Species control capacity $\phi$ was only weakly correlated with commonly-used centrality metrics. 
The Spearman correlation between these ranged between `r round(min(correlations$control_capacity), 2)` (with betweeness-centrality) and `r round(max(correlations$control_capacity), 2)` (with eigen-centrality), see Figure \@ref(S-fig:fig-correlogram)a. 
The correlation coefficient with degree was `r round(correlations[correlations$rowname == "degree", ]$control_capacity, 2)`, however most species with high degree also tended to attain a high control capacity (Figure \@ref(S-fig:fig-species-models-degree)a).
